---
title: "Analyses"
output: pdf_document
---

\pagenumbering{gobble}
\pagebreak
\tableofcontents
\pagebreak

\pagebreak
\pagenumbering{arabic}

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE, fig.width=4, fig.height=4, fig.align = "center")
```

---

# Description of scripts: 

* Social_Media_Processing.R imports the different data files, joins them together into single dataframes,
binarizes the liwc-files, excludes dates that do not belong into the baseline date range
and finally excludes twitter related posts that were either categorized as originating from
organizations by Brandwatch or were posted by users with below 100 or beyond 5000 followers.
* Survey_Processing.R pre-processes the survey data and groups important variables together.
* Social_Media_Baseline_1.R integrates the datafiles created by Social_Media_Processing.R and the date-related information of the survey, and baseline-corrects the 2020 twitter gs and liwc values with mean weekday values of 2019. 
* The data in the "data/" file represents the output of the
Social_Media_Baseline_1.R file and comprises the baseline-corrected variables per survey wave for 
    1) negative and positive gs twitter scores, 
    2) positive emotion, negative emotion, anxiety, anger, sad and social liwc twitter scores.
* Social_Media_Baseline_2.R baseline-corrects the 2020 twitter GS and LIWC values grouped by federal state.


# Analyses

```{r Libraries, echo = FALSE}
library(tidyverse)
library(data.table)
library(psych) # mixed factor analyses
library(gridExtra)
library(ggcorrplot)
library(boot) 
library(rlist) # subsetting lists
library(leaps) # needed for bestglm
library(bestglm) # package for best subset selection
library(dummies) # create dummy variables
library(GGally) 
library(papaja)
library(ggDoE) # for diagnostic plots
library(ppcor) # computed partial correlations
```

```{r Import Data, echo = FALSE, message = FALSE}
# Import baseline-corrected DerStandard and Twitter data for different timeframes

# Import a list that contains each baseline-correction for differing time spans: from -14 days:75% responded to -1 day:75% responded:
# For DerStandard
load("../data/liwc_stand_corrected_time.RData")
load("../data/gs_stand_corrected_time.RData")

# For Twitter
load("../data/liwc_twitter_corrected_time.RData")
load("../data/gs_twitter_corrected_time.RData")

# Import baseline-corrected twitter data for each gender and federal state
load("../data/liwc_federal_gender.RData")
load("../data/gs_federal_gender.RData")


# These dataframes are indeed containing all of the following whose time span ends when 75% of the participants responded. 

#############################################################################
# _anx data belongs to the analyses concerning anxiety and anger (-7 days prior to survey onset)
# _depr data belongs to the analyses concerning depression (-14 days prior to survey onset)

# Import baseline-corrected DerStandard data
load("../data/gs_stand_corrected_anx.RData")
load("../data/gs_stand_corrected_depr.RData")
load("../data/liwc_stand_corrected_anx.RData")
load("../data/liwc_stand_corrected_depr.RData")

# Import baseline-corrected Twitter data
load("../data/gs_twitter_corrected_anx.RData")
load("../data/gs_twitter_corrected_depr.RData")
load("../data/liwc_twitter_corrected_anx.RData")
load("../data/liwc_twitter_corrected_depr.RData")


#############################################################################
# 1:14 days prior to survey onset until 50% of the participants responded (for varying starting points)
# Import baseline-corrected DerStandard data
load("../data/liwc_stand_corrected_time_50.RData")
load("../data/gs_stand_corrected_time_50.RData")

# Import baseline-corrected Twitter data
load("../data/liwc_twitter_corrected_time_50.RData")
load("../data/gs_twitter_corrected_time_50.RData")

#############################################################################
```

# Analyses for whole Austria

## Computation of survey-values
```{r}
# survey data: only including the first 75% of participants each survey wave 
load("../data/d2_vars.Rdata")

# survey data: only including the first 50% of participants each survey wave 
load("../data/d2_vars_50.Rdata")
```

## Correlation Table: Survey (anxiety, anger, depression) vs. sentiment scores)
First of all, a correlation table is computed that includes Spearman rank correlations between the anxiety, anger and depression survey constructs and the respective sentiment scores, i.e. the anxiety, anger and sadness LIWC score and the negative emotionality GS score. Specifically, this analysis follows the idea of the pre-registration: The chosen time-frames for anxiety and anger range from seven days prior to each survey wave onset until 75% of the participants responded to this survey. All Twitter and Der Standard postings that fall into this time-frame are included in the correlation analyses. For the survey depression construct all postings from 14 days prior to each survey wave onset until 75% of the participants responded to this survey were included. These time-frames (7 days and 14 days prior to survey onset) correspond to how far the respective scale's items refer back in time.  


```{r}
# initialize a list that will store all the relevant results
results_main <- vector(mode = "list", length = 4)
names(results_main) <- c("Results Twitter - Fisher z-transformation", 
                         "Results Twitter - Nonparametric bootstrap", 
                         "Results DerStandard - Fisher z-transformation", 
                         "Results DerStandard - Nonparametric bootstrap")

# Twitter data:
# bind important variables together into one dataframe
data_corr_twitter <- cbind.data.frame(d2_vars[, 2:4], 
                                      gs_twitter_corrected_anx[, 5], 
                                      liwc_twitter_corrected_anx[, 10:11],
                                      liwc_twitter_corrected_depr[, 12])
names(data_corr_twitter) <- c("Anx Surv", "Depr Surv", "Anger Surv", "Neg GS", 
                              "Anx", "Anger", "Sad")

# Der Standard data:
data_corr_stand <- cbind.data.frame(d2_vars[, 2:4], 
                                      gs_stand_corrected_anx[, 5], 
                                      liwc_stand_corrected_anx[, 10:11],
                                      liwc_stand_corrected_depr[, 12])
names(data_corr_stand) <- c("Anx Surv", "Depr Surv", "Anger Surv", "Neg GS", 
                              "Anx", "Anger", "Sad")


# compute the confidence interval for rho using an adaption of the Fisher z-transformation as proposed by Bonnett and Wright (2000) and further developed by Ruscio (2008)
# alpha is set to 0.10 in the consequent analyses, since our hypothesis test
# is one-sided on a 0.050 level. I will report both confidence bounds (lower and upper) but the lower bound is the most interesting since the hypotheses are only rejected if the lower bound of the confidence interval is greater than 0. 

spearman_CI <- function(x, y, alpha = 0.10, index = TRUE, subset = c(1:4, 9, 11), seed = 1234){
  # This function outputs Spearman's rank correlations as well as p-values and confidence intervals computed by an adaptation of a      Fisher z-transformation as well as confidence intervals computed by a nonparametric bootstrap. Moreover it outputs the full          correlation matrix for further plots.
  
  # Spearman's rank correlation coefficient
  spear_r <- cor(x, y, use = "complete.obs", method = "spearman")
  # save spear_r that entails all possible correlations for potential correlation table plots
  spear_r_complete <- spear_r
  
  # names for correlations
  names <- c(paste(row.names(spear_r_complete), colnames(spear_r_complete)[1]),                                      paste(row.names(spear_r_complete)[c(1, 3, 2)], colnames(spear_r_complete)[2:4]))
  
  # Number of observations
  n <- sum(complete.cases(x, y))
  
  # compute one-tailed p-value (see Ruscio (2008) for standard error estimation)
  p <- 1- pt(atanh(spear_r)/sqrt((1 + spear_r^2/2)/(n - 3)), df = n - 2)
  
  # p_2 would be the one-tailed p-value for the "standard" Fisher z-transformation
  #p_2 <- 1- pnorm(q = atanh(spear_r), mean = 0, sd = 1/sqrt(n - 3))
                
  # Upper and lower confidence interval limit
  # Holm-Bonferroni correction if index = TRUE
  if(index == FALSE){
    CI_upper <- tanh(atanh(spear_r) - sqrt((1 + spear_r^2/2)/(n - 3))
            * qt(p = alpha/2, df = n - 2))
  
    CI_lower <- tanh(atanh(spear_r) + sqrt((1 + spear_r^2/2)/(n - 3))
            * qt(p = alpha/2, df = n - 2))
  }
  
  if(index == TRUE){
    # subset correlations that are necessary, and compute Holm-Bonferroni adjusted confidence intervals
    p <- p[subset]
    order_data <- rank(p, ties.method = "first") # in order to re-subset the original order
    order_p <- order(p)
    names <- names[order_p]

    p <- p[order_p]
    spear_r <- spear_r[subset][order_p]
    names(p) <- names
    names(spear_r) <- names
    
    # number of hypothesis to be tested
    m <- length(spear_r)
    
    # Bootstrapping:
    boot_spear <- function(data, indices, a, b) {
      # subset rows of given data matrix
      d <- data[indices, ]
      # compute Spearman rank correlation coefficient
      r <- round(as.numeric(cor(d[a], d[b], method = "spearman")), 3)
      # output r
      r
    }

    # set seed for reproducibility
    set.seed(seed)
    temp_1 <- c(colnames(x), colnames(x)[c(1, 3, 2)])
    temp_2 <- c(rep(colnames(y)[1], 3), colnames(y)[2:4])

    # initialize list for resulting bootstrap outputs
    boot_results <- vector(mode = "list", length = m)
    plot_boot <- vector(mode = "list", length = m)
    
    for(i in 1:m){
      boot_results[[i]] <- boot(
      data = cbind(x, y),
      a = temp_1[i], 
      b = temp_2[i], 
      R = 5000,
      statistic = boot_spear)
      
      if(i == 1){ boot_r <- boot_results[[1]]$t}
      if(i != 1){boot_r <- cbind(boot_r, boot_results[[i]]$t)}
      # save distribution and qqplots of bootstraps
      #boot_t <- lapply(boot_results, function(x) {x[["t"]]}) # each sample
      plot_boot[[i]] <- plot(boot_results[[i]]) # outputs both histogram and qq-plot
    }
    
    names(plot_boot) <- names[order_data]
    colnames(boot_r) <- names[order_data]

    # for-loop to compute adjusted confidence intervals
    #initiallize vectors for bootstrap CI
    CI_boot <- matrix(NA, nrow = m, ncol = 3)

    for(i in 1:m){
      # Woods (2007)
      CI_upper_Z <- tanh(atanh(spear_r) - sqrt((1 + spear_r^2/2)/(n - 3))
            * qt(p = alpha/(2 * (m + 1 - i)), df = n - 2))
  
      CI_lower_Z <- tanh(atanh(spear_r) + sqrt((1 + spear_r^2/2)/(n - 3))
            * qt(p = alpha/(2 * (m + 1 - i)), df = n - 2))
      
      # Bootstrap
      boot_output <- boot.ci(boot_results[[i]], conf = 1 - alpha/((m + 1 - i)))
      CI_boot[i, ] <- boot_output$percent[c(1, 4, 5)]
    }
  }
  
  # cbind rho, p, CI_lower and CI_upper
  summary_rho <- round(cbind(spear_r[order_data], CI_boot[, 1], 
                       cbind(CI_lower_Z, CI_upper_Z, p)[order_data, ]), 3)
  colnames(summary_rho) <- c("Rho", "Confidence", "Lower adj", "Upper adj", "p")
  
  summary_rho_boot <- round(cbind(spear_r[order_data], CI_boot), 3)
  colnames(summary_rho_boot) <- c("Rho", "Confidence", "Lower adj", "Upper adj")
  
  
  # Return Spearman's Rho, confidence interval bounds and p-value
  invisible(list(summary_rho_Z = summary_rho,
              summary_rho_boot = summary_rho_boot,
              rho_complete = spear_r_complete,
              plot_boot = plot_boot,
              boot_r = boot_r))
}

# Compute Rho, confidence intervals and p
spear_twitter <- spearman_CI(x = data_corr_twitter[, 1:3], y = data_corr_twitter[, 4:7])

# Twitter z-transform
results_main[[1]] <- spear_twitter$summary_rho_Z
# Twitter bootstrap
results_main[[2]] <- spear_twitter$summary_rho_boot


spear_stand <- spearman_CI(x = data_corr_stand[, 1:3], y = data_corr_stand[, 4:7])
# DerStandard z-transform
results_main[[3]] <- spear_stand$summary_rho_Z
# DerStandard bootstrap
results_main[[4]] <- spear_stand$summary_rho_boot

save(results_main, file = "../data/results_main.Rdata")
save(spear_twitter, file = "../data/spear_twitter.Rdata")
save(spear_stand, file = "../data/spear_stand.Rdata")

# load("../data/results_main.Rdata")
# load("../data/spear_twitter.Rdata")
# load("../data/spear_stand.Rdata")

# call plots (histogram and qq-plot for each computed bootstrap)
#lapply(spear_twitter$plot_boot, plot)
# lapply(spear_stand$plot_boot, plot)
```



Histograms and qq-plots of bootstrap samples:
```{r, fig.width = 11, fig.heigth = 10}
# since normal plot(boot_object) function does not contain a title in order to differentiate between different plots, ggplots for histogram and qq-plots arec reated

# change matrix to dataframe for ggplot
spear_twitter$boot_r <- as.data.frame(spear_twitter$boot_r)
# sub " " with "_" in order to be able to read in and evaluate colnames directly in ggplot aes settings.
colnames(spear_twitter$boot_r) <- gsub(pattern = " ",replacement = "_", x = names(spear_twitter$boot_r))

spear_stand$boot_r <- as.data.frame(spear_stand$boot_r)
# NAMES ARE WRONG: names(spear_stand$boot_r) HAS A DUPLICATE!
colnames(spear_stand$boot_r) <- gsub(pattern = " ",replacement = "_", x = names(spear_stand$boot_r))

# create histogram and ggplot for all six Twitter/DerStandard bootstrap samples

twitter_hist <- lapply(1:nrow(spear_twitter$summary_rho_Z), function(.x) {ggplot(data = spear_twitter$boot_r, eval(parse(text = paste("aes(x = ", colnames(spear_twitter$boot_r)[.x], ")")))) + 
  geom_histogram(col = I("red"), fill = I("blue"), alpha=I(.2), binwidth = 0.03)+
  labs(title = paste("Histogram of", "\u03C1", row.names(spear_twitter$summary_rho_boot)[.x])) +
  xlab(paste("\u03C1", row.names(spear_twitter$summary_rho_boot)[.x])) +
  theme_bw() +
  theme(plot.title = element_text(size = 9)) +
  geom_vline(xintercept = spear_twitter$summary_rho_Z[.x, 1])})


twitter_qq <- lapply(1:nrow(spear_twitter$summary_rho_Z), function(.x) {ggplot(data = spear_twitter$boot_r, eval(parse(text = paste("aes(sample = ", colnames(spear_twitter$boot_r)[.x], ")")))) +
  stat_qq() +
  stat_qq_line() +
  theme_bw() +
  labs(title = "QQ-Plot")})


stand_hist <- lapply(1:nrow(spear_stand$summary_rho_Z), function(.x) {ggplot(data = spear_stand$boot_r, eval(parse(text = paste("aes(x = ", colnames(spear_stand$boot_r)[.x], ")")))) + 
  geom_histogram(col = I("red"), fill = I("blue"), alpha=I(.2), binwidth = 0.03)+
  labs(title = paste("Histogram of", "\u03C1", row.names(spear_stand$summary_rho_boot)[.x])) +
  xlab(paste("\u03C1", row.names(spear_stand$summary_rho_boot)[.x])) +
  theme_bw() +  
  theme(plot.title = element_text(size = 9)) +
  geom_vline(xintercept = spear_stand$summary_rho_Z[.x, 1])})


stand_qq <- lapply(1:nrow(spear_stand$summary_rho_Z), function(.x) {ggplot(data = spear_stand$boot_r, eval(parse(text = paste("aes(sample = ", colnames(spear_stand$boot_r)[.x], ")")))) +
  stat_qq() +
  stat_qq_line() +
  theme_bw() +
  labs(title = "QQ-Plot")})

# grid.arrange(grobs = twitter_hist, ncol = 3)
# grid.arrange(grobs = twitter_qq, ncol = 3)


#grid.arrange(grobs = c(twitter_hist, twitter_qq), ncol = 4)

# load package
# rearrange corresponding histrogram and qq-plots next to one another.
list_twitter <- list.subset(c(twitter_hist, twitter_qq), c(1, 7, 2, 8, 3, 9, 4, 10, 5, 11, 6 , 12))

histboottwitter_anx_GS <-  grid.arrange(grobs = list_twitter[1:2], ncol = 2)
histboottwitter_ang_GS <-  grid.arrange(grobs = list_twitter[5:6], ncol = 2)
histboottwitter_depr_GS <-  grid.arrange(grobs = list_twitter[3:4], ncol = 2)
histboottwitter_anx_LIWC <-  grid.arrange(grobs = list_twitter[7:8], ncol = 2)
histboottwitter_ang_LIWC <-  grid.arrange(grobs = list_twitter[9:10], ncol = 2)
histboottwitter_depr_LIWC <-  grid.arrange(grobs = list_twitter[11:12], ncol = 2)

ggsave("../plots/histboottwitter_anx_GS.png", histboottwitter_anx_GS, width = 5, height = 3.5)
ggsave("../plots/histboottwitter_ang_GS.png", histboottwitter_ang_GS, width = 5, height = 3.5)
ggsave("../plots/histboottwitter_depr_GS.png", histboottwitter_depr_GS, width = 5, height = 3.5)
ggsave("../plots/histboottwitter_anx_LIWC.png", histboottwitter_anx_LIWC, width = 5, height = 3.5)
ggsave("../plots/histboottwitter_ang_LIWC.png", histboottwitter_ang_LIWC, width = 5, height = 3.5)
ggsave("../plots/histboottwitter_depr_LIWC.png", histboottwitter_depr_LIWC, width = 5, height = 3.5)


# histboottwitter <- grid.arrange(grobs = list_twitter, ncol = 4)
# ggsave("../plots/histboottwitter.png", histboottwitter, width = 11, height = 12)

list_stand <- list.subset(c(stand_hist, stand_qq), c(1, 7, 2, 8, 3, 9, 4, 10, 5, 11, 6 , 12))

histbootstand_anx_GS <-  grid.arrange(grobs = list_stand[1:2], ncol = 2)
histbootstand_ang_GS <-  grid.arrange(grobs = list_stand[5:6], ncol = 2)
histbootstand_depr_GS <-  grid.arrange(grobs = list_stand[3:4], ncol = 2)
histbootstand_anx_LIWC <-  grid.arrange(grobs = list_stand[7:8], ncol = 2)
histbootstand_ang_LIWC <-  grid.arrange(grobs = list_stand[9:10], ncol = 2)
histbootstand_depr_LIWC <-  grid.arrange(grobs = list_stand[11:12], ncol = 2)

ggsave("../plots/histbootstand_anx_GS.png", histbootstand_anx_GS, width = 5, height = 3.5)
ggsave("../plots/histbootstand_ang_GS.png", histbootstand_ang_GS, width = 5, height = 3.5)
ggsave("../plots/histbootstand_depr_GS.png", histbootstand_depr_GS, width = 5, height = 3.5)
ggsave("../plots/histbootstand_anx_LIWC.png", histbootstand_anx_LIWC, width = 5, height = 3.5)
ggsave("../plots/histbootstand_ang_LIWC.png", histbootstand_ang_LIWC, width = 5, height = 3.5)
ggsave("../plots/histbootstand_depr_LIWC.png", histbootstand_depr_LIWC, width = 5, height = 3.5)


# histbootstand <- grid.arrange(grobs = list_stand, ncol = 4)
# # pdf does not work for unicode characters are used to exhibit rho as Greek letter
# ggsave("../plots/histbootstand.png", histbootstand, width = 11, height = 12)
```


Correlation Matrix visualizations:
```{r, fig.width=9, warning = FALSE, message = FALSE}
# Visualizing the correlation matrix using 
# square and circle methods
#ggcorrplot(corrp.mat, method ="square", type = "lower", lab = TRUE)
df_twitter <- spear_twitter$rho_complete
df_stand <- spear_stand$rho_complete


# only display "main" correlations of interest
# df_twitter[-c(1:4, 9, 11)] <- NA
# df_stand[-c(1:4, 9, 11)] <- NA

plot_twitter <- ggcorrplot(t(df_twitter), method ="circle", lab = TRUE)
plot_stand <- ggcorrplot(t(df_stand), method ="circle", lab = TRUE)

ggsave("../plots/cortable_twitter.pdf", plot_twitter, width = 4.5, height = 3)
ggsave("../plots/cortable_stand.pdf", plot_stand, width = 4.5, height = 3)

# compute plot of differences: For these correlations of for all correlations (symmetric matrix for visual inspection):
# corr_table_diff <- ggcorrplot(t(df_twitter) - t(df_stand), method ="circle", lab = TRUE, title = "\u0394 \u03C1 Twitter - Standard")
```


Next, Spearman's rank correlation coefficients are computed between the same constructs but as a function of the time window we used to include the social media data for the calculation of the emotion and sentiment measures. The final point for each survey wave is fixed on the value that was pre-registered at first. This means for each survey wave, the date until 75% of the participants responded to the survey is fixed and all data-points of the survey until this point are included. For the sentiment scores we vary the included time-frame from 14 days to 1 day prior to survey onset until this fixed date the last of the 75% participants responded to the survey.
```{r}
# # For DerStandard
# load("../data/liwc_stand_corrected_time.RData")
# load("../data/gs_stand_corrected_time.RData")
# # For Twitter
# load("../data/liwc_twitter_corrected_time.RData")
# load("../data/gs_twitter_corrected_time.RData")
# # survey data: only including the first 75% of participants each survey wave 
# load("../data/d2_vars.Rdata")

# compute Spearman's rho for differing time spans
# Twitter
liwc_twitter_rho <- lapply(1:14, function(.x) {cor(d2_vars[, 2:4], 
                                                 cbind(gs_twitter_corrected_time[[.x]]
                               [, "negative.corrected"],liwc_twitter_corrected_time[[.x]]
                               [, c("Anx.corrected", "Sad.corrected", 
                                    "Anger.corrected")]), 
                               method = "spearman", use = "complete.obs")})

liwc_twitter_rho <- t(sapply(liwc_twitter_rho, FUN = "[", c(1:4, 8, 12)))

# add column names
#load("../data/results_main.Rdata")
colnames(liwc_twitter_rho) <- row.names(results_main[[1]])[c(1:4, 6, 5)]


# DerStandard
liwc_stand_rho <- lapply(1:14, function(.x) {cor(d2_vars[, 2:4], 
                                                 cbind(gs_stand_corrected_time[[.x]]
                               [, "negative.corrected"],liwc_stand_corrected_time[[.x]]
                               [, c("Anx.corrected", "Sad.corrected", 
                                    "Anger.corrected")]), 
                               method = "spearman", use = "complete.obs")})

liwc_stand_rho <- t(sapply(liwc_stand_rho, FUN = "[", c(1:4, 8, 12)))

# add column names
colnames(liwc_stand_rho) <- colnames(liwc_twitter_rho)

# for comparison: anger and anxiety: -7 days, depression: - 14 days
# round(liwc_stand_rho[c(7, 14), ], 3)
# results_main[[3]][, 1]

# add time lag variable as first column and transform to df for plots 
liwc_twitter_rho <- data.frame(lag = 1:14, liwc_twitter_rho)
liwc_stand_rho <- data.frame(lag = 1:14, liwc_stand_rho)


# plot development of Spearman's Rho as a function of time lag

# settings ####
labelsize <- 11
axisfontsize <- 10
emo_cols <- c("Anx Surv Neg GS" ="red", 
              "Depr Surv Neg GS"="steelblue4",
              "Anger Surv Neg GS" = "orange",
              "Anx Surv Anx" = "red4",
              "Depr Surv Sad"="steelblue2",
              "Anger Surv Anger" = "yellow")

# pivot for ggplot
liwc_twitter_rho <- pivot_longer(liwc_twitter_rho, cols = 2:7)

liwc_stand_rho <- pivot_longer(liwc_stand_rho, cols = 2:7)


# Twitter
plt_twitter_lag <- ggplot() +
  geom_line(data = liwc_twitter_rho, aes(x = lag, y= value, 
                                            colour = name,  linetype = name), 
            alpha = 0.6, size = 0.8)+
  ylab("Spearman's \u03C1")  +
  xlab("Time-Lag in Days") +
  #ggtitle("Twitter") +
  scale_x_continuous(breaks = 1:14) +
  theme_bw()+ theme(text=element_text(size=axisfontsize), axis.text=element_text(size=labelsize), 
                    #axis.title.x = element_blank(),
                    legend.title=element_blank(), legend.position="bottom",
                    legend.text = element_text(size=6.5),
                    legend.key.size = unit(1.5,"line"),
                    plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))+
  theme(plot.title = element_text(size = 10))+
  guides(color=guide_legend(nrow=2, byrow=TRUE),
         shape = guide_legend(override.aes = list(size = 2)))
  
#plt_twitter_lag

# Der Standard
plt_stand_lag <- ggplot() +
  geom_line(data = liwc_stand_rho, aes(x = lag, y= value, 
                                            colour = name,  linetype = name), 
            alpha = 0.6, size = 0.8)+
  ylab("Spearman's \u03C1")  +
  xlab("Time-Lag in Days") +
  #ggtitle("Der Standard") +
  scale_x_continuous(breaks = 1:14) +
  theme_bw()+ theme(text=element_text(size=axisfontsize), axis.text=element_text(size=labelsize), 
                    #axis.title.x = element_blank(),
                    legend.title=element_blank(), legend.position="bottom",
                    legend.text = element_text(size=6.5),
                    legend.key.size = unit(1.5,"line"),
                    plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))+
  theme(plot.title = element_text(size = 10))+
  guides(color=guide_legend(nrow=2, byrow=TRUE),override.aes = list(size = 2))#+
  #guides(shape = guide_legend(override.aes = list(size = 4)))
         
ggsave("../plots/plt_twitter_lag.png", plt_twitter_lag, width = 10, height = 4.5)
ggsave("../plots/plt_stand_lag.png", plt_stand_lag, width = 10, height = 4.5)

#plt_stand_lag

# if one decides to show these two plots next to one another: decrease size of title
# plt_lag <- grid.arrange(plt_twitter_lag, plt_stand_lag, nrow = 2)
# ggsave("../plots/plotlag.pdf", plt_lag, width = 10, height = 4.5)
```

Same correlation time series plot but now using "_50" data: only including the first 50% of the respondents to the survey:
```{r}
# # For DerStandard
# load("../data/liwc_stand_corrected_time_50.RData")
# load("../data/gs_stand_corrected_time_50.RData")
# # For Twitter
# # Import baseline-corrected Twitter data
# load("../data/liwc_twitter_corrected_time_50.RData")
# load("../data/gs_twitter_corrected_time_50.RData")
# # survey data: only including the first 50% of participants each survey wave
# load("../data/d2_vars_50.Rdata")

# compute Spearman's rho for differing time spans
# Twitter
liwc_twitter_rho_50 <- lapply(1:14, function(.x) {cor(d2_vars_50[, 2:4], 
                                                 cbind(gs_twitter_corrected_time_50[[.x]]
                               [, "negative.corrected"],liwc_twitter_corrected_time_50[[.x]]
                               [, c("Anx.corrected", "Sad.corrected", 
                                    "Anger.corrected")]), 
                               method = "spearman", use = "complete.obs")})

liwc_twitter_rho_50 <- t(sapply(liwc_twitter_rho_50, FUN = "[", c(1:4, 8, 12)))

# add column names
#load("../data/results_main.Rdata")
colnames(liwc_twitter_rho_50) <- row.names(results_main[[1]])[c(1:4, 6, 5)]

# DerStandard
liwc_stand_rho_50 <- lapply(1:14, function(.x) {cor(d2_vars_50[, 2:4], 
                                                 cbind(gs_stand_corrected_time_50[[.x]]
                               [, "negative.corrected"],liwc_stand_corrected_time_50[[.x]]
                               [, c("Anx.corrected", "Sad.corrected", 
                                    "Anger.corrected")]), 
                               method = "spearman", use = "complete.obs")})

liwc_stand_rho_50 <- t(sapply(liwc_stand_rho_50, FUN = "[", c(1:4, 8, 12)))

# add column names
colnames(liwc_stand_rho_50) <- colnames(liwc_twitter_rho_50)

# add time lag variable as first column and transform to df for plots 
liwc_twitter_rho_50 <- data.frame(lag = 1:14, liwc_twitter_rho_50)
liwc_stand_rho_50 <- data.frame(lag = 1:14, liwc_stand_rho_50)


# plot development of Spearman's Rho as a function of time lag
# settings
labelsize <- 11
axisfontsize <- 10
emo_cols <- c("Anx Surv Neg GS" ="red", 
              "Depr Surv Neg GS"="steelblue4",
              "Anger Surv Neg GS" = "orange",
              "Anx Surv Anx" = "red4",
              "Depr Surv Sad"="steelblue2",
              "Anger Surv Anger" = "yellow")

# to dataframe for ggplot
liwc_twitter_rho_50 <- pivot_longer(liwc_twitter_rho_50, cols = 2:7)

liwc_stand_rho_50 <- pivot_longer(liwc_stand_rho_50, cols = 2:7)

# Twitter
plt_twitter_lag_50 <- ggplot() +
  geom_line(data = liwc_twitter_rho_50, aes(x = lag, y= value, 
                                            colour = name,  linetype = name), 
            alpha = 0.6, size = 0.8)+
  ylab("Spearman's \u03C1")  +
  xlab("Time-Lag in Days") +
  #ggtitle("Twitter") +
  scale_x_continuous(breaks = 1:14) +
  theme_bw()+ theme(text=element_text(size=axisfontsize), axis.text=element_text(size=labelsize), 
                    #axis.title.x = element_blank(),
                    legend.title=element_blank(), legend.position="bottom",
                    legend.text = element_text(size=6.5),
                    legend.key.size = unit(2,"line"),
                    plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))+
  theme(plot.title = element_text(size = 10))+
  guides(color=guide_legend(nrow=2, byrow=TRUE))
  

#plt_twitter_lag_50

# Der Standard
plt_stand_lag_50 <- ggplot() +
  geom_line(data = liwc_stand_rho_50, aes(x = lag, y= value, 
                                            colour = name,  linetype = name), 
            alpha = 0.6, size = 0.8)+
  ylab("Spearman's \u03C1")  +
  xlab("Time-Lag in Days") +
  #ggtitle("Der Standard") +
  scale_x_continuous(breaks = 1:14) +
  theme_bw()+ theme(text=element_text(size=axisfontsize), axis.text=element_text(size=labelsize), 
                    #axis.title.x = element_blank(),
                    legend.title=element_blank(), legend.position="bottom",
                    legend.text = element_text(size=6.5),
                    legend.key.size = unit(2,"line"),
                    plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))+
  theme(plot.title = element_text(size = 10))+
  guides(color=guide_legend(nrow=2, byrow=TRUE))
  
# plt_stand_lag_50
ggsave("../plots/plt_twitter_lag_50.png", plt_twitter_lag_50, width = 10, height = 4.5)
ggsave("../plots/plt_stand_lag_50.png", plt_stand_lag_50, width = 10, height = 4.5)

# if one decides to show these two plots next to one another: decrease size of title
# plt_lag_50 <-grid.arrange(plt_twitter_lag_50, plt_stand_lag_50, nrow = 2)
# ggsave("../plots/plotlag_50.pdf", plt_lag_50, width = 9, height = 9)
```


# Analyses split by gender and federal-state

## Multiple linear regression: Linear influence of sentiment measures over and above demographic variables
Since demographic information concerning gender and federal states are mostly available for Twitter postings, we like to investigate whether our sentiment measures (i.e. GermanSentiment or LIWC) still play a prominent role in explaining the survey scales when firstly controlling for gender and federal state. This will be achieved by employing multiple linear regression analyses.
Eventhough the data sample is limited, the assumptions of the linear model, i.e. the corresponding residuals, are analyzed.

```{r}
# import data
load("../data/liwc_federal_gender.RData")
load("../data/gs_federal_gender.RData")
# survey data: only including the first 75% of participants each survey wave 
load("../data/d2_vars_federal.RData")

# for anger, anxiety analyes -7 days-75% responded, for depression -14 days - 75 %
# create dataframe
df_regression <- cbind.data.frame(gs_federal_gender[[7]][, 1:3], d2_vars_federal[, 4:6], gs_federal_gender[[7]]['negative.corrected'], liwc_federal_gender[[7]][, 12:13], liwc_federal_gender[[14]]['Sad.corrected'])

# change column names
names(df_regression)[2:ncol(df_regression)] <- c("Region", "Gender", "Anxiety", "Depression", "Anger", "GS_Negative", "LIWC_Anxiety", "LIWC_Anger", "LIWC_Sadness")
```


### Anxiety GS (-7 days - 75% responded) 

```{r}
set.seed(100)
# Hierarchical regression: survey anxiety construct
# null model: only containing demographic variables
reg_anx_null <- lm(Anxiety ~ Gender + Region, data = df_regression)
# full model: now include negative.corrected 
reg_anx_full <- update(reg_anx_null, formula = . ~ . + GS_Negative)

# print and save diagnostic plots for full model
# pairs_hist(df_regression[,c("Region", "Gender", "Anxiety", "GS_Negative")])
# pairs(df_regression[,c("Region", "Gender", "Anxiety", "GS_Negative")])

# partial correlation plot
# explain in the dependent variable after removing sysematic variation explained by gender and federal state with the part of independent variable (sentiment measure) uncorrelated with Gender and Region
Y_resid_anx_GS <- resid(reg_anx_null) 
X_resid_GS <- resid(lm(GS_Negative ~ Gender + Region, df_regression))

pcp_anxiety_GS <- ggplot(df_regression, aes(x = X_resid_GS, y = Y_resid_anx_GS)) +
  geom_point() +
  labs(x="GS Negative | Gender + Region", y = "Anxiety | Gender + Region")+
  theme_bw() +
  geom_smooth(method = lm)

#pcp_anxiety_GS
ggsave("../plots/pcp_anxiety_GS.pdf", pcp_anxiety_GS, width = 5, height = 3.5)

diagnostic_anx_GS <- diagnostic_plots(reg_anx_full)
ggsave("../plots/diagnostic_anx_GS.pdf", diagnostic_anx_GS, width = 5.2, height = 3.5)

# calculate and print model comparison, bootstrap for CI R^2
anova_anx_GS <- apa_print(list(Baseline = reg_anx_null, 'GS Negative' = 
                                 reg_anx_full), boot_samples = 2000)

save(anova_anx_GS, file = "../data/anova_anx_GS.RData")
```


### Anger GS (-7 days - 75% responded) 

```{r}
set.seed(100)
# Hierarchical regression: survey anger construct
# null model: only containing demographic variables
reg_ang_null <- lm(Anger ~ Gender + Region, data = df_regression)
# full model: now include negative.corrected
reg_ang_full <- update(reg_ang_null, formula = . ~ . + GS_Negative)

# print and save diagnostic plots for full model
# pairs(df_gs[,c("Region", "Gender", "Anger", "GS_Negative")])

# partial correlation plot
Y_resid_ang_GS <- resid(reg_ang_null) 

pcp_anger_GS <- ggplot(df_regression, aes(x = X_resid_GS, y = Y_resid_ang_GS)) +
  geom_point() +
  labs(x="GS Negative | Gender + Region", y = "Anger | Gender + Region")+
  theme_bw() +
  geom_smooth(method = lm)

#pcp_anger_GS
ggsave("../plots/pcp_anger_GS.pdf", pcp_anger_GS, width = 5, height = 3.5)

diagnostic_ang_GS <- diagnostic_plots(reg_ang_full)
ggsave("../plots/diagnostic_ang_GS.pdf", diagnostic_ang_GS, width = 5.2, height = 3.5)

# calculate and print model comparison, bootstrap for CI R^2
anova_ang_GS <- apa_print(list(Baseline = reg_ang_null, 'GS Negative' = 
                                 reg_ang_full), boot_samples = 2000)
save(anova_ang_GS, file = "../data/anova_ang_GS.RData")
```


### Depression GS (-14 days - 75% responded) 

```{r}
set.seed(100)
# Hierarchical regression: survey depression construct
# null model: only containing demographic variables
reg_depr_null <- lm(Depression ~ Gender + Region, data = df_regression)
# full model: now include negative.corrected
reg_depr_full <- update(reg_depr_null, formula = . ~ . + GS_Negative)

# print and save diagnostic plots for full model
# pairs(df_gs[,c("Region", "Gender", "Depression", "GS_Negative")])

# partial correlation plot
Y_resid_depr_GS <- resid(reg_depr_null) 

pcp_depr_GS <- ggplot(df_regression, aes(x = X_resid_GS, y = Y_resid_depr_GS)) +
  geom_point() +
  labs(x="GS Negative | Gender + Region", y = "Depression | Gender + Region")+
  theme_bw() +
  geom_smooth(method = lm)

#pcp_depr_GS
ggsave("../plots/pcp_depr_GS.pdf", pcp_depr_GS, width = 5, height = 3.5)

diagnostic_depr_GS <- diagnostic_plots(reg_depr_full)
ggsave("../plots/diagnostic_depr_GS.pdf", diagnostic_depr_GS, width = 5.2, height = 3.5)

# calculate and print model comparison, bootstrap for CI R^2
anova_depr_GS <- apa_print(list(Baseline = reg_depr_null, 'GS Negative' = 
                                 reg_depr_full), boot_samples = 2000)
save(anova_depr_GS, file = "../data/anova_depr_GS.RData")
```



### Anxiety LIWC (-7 days - 75% responded) 

```{r}
set.seed(100)
# Hierarchical regression: survey anxiety construct
# null model already computed above: reg_anx_null
# full model: now include Anx.corrected
reg_anx_full <- update(reg_anx_null, formula = . ~ . + LIWC_Anxiety)

# print and save diagnostic plots for full model
#pairs(df_liwc[,c("Region", "Gender", "Anxiety", "LIWC_Anxiety")])

# partial correlation plot
X_resid_anx_LIWC <- resid(lm(LIWC_Anxiety ~ Gender + Region, df_regression))
Y_resid_anx_LIWC <- resid(reg_anx_null) 

pcp_anxiety_LIWC <- ggplot(df_regression, aes(x = X_resid_anx_LIWC, y = Y_resid_anx_LIWC)) +
  geom_point() +
  labs(x="LIWC Anxiety | Gender + Region", y = "Anxiety | Gender + Region")+
  theme_bw() +
  geom_smooth(method = lm)

#pcp_anxiety_LIWC
ggsave("../plots/pcp_anxiety_LIWC.pdf", pcp_anxiety_LIWC, width = 5, height = 3.5)

diagnostic_anx_LIWC <- diagnostic_plots(reg_anx_full)
ggsave("../plots/diagnostic_anx_LIWC.pdf", diagnostic_anx_LIWC, width = 5.2, height = 3.5)

# calculate and print model comparison, bootstrap for CI R^2
anova_anx_LIWC <- apa_print(list(Baseline = reg_anx_null, 'LIWC Anxiety' = 
                                 reg_anx_full), boot_samples = 2000)

save(anova_anx_LIWC, file = "../data/anova_anx_LIWC.RData")
```


### Anger LIWC (-7 days - 75% responded) 

```{r}
set.seed(100)
# Hierarchical regression: survey anger construct
# null model already computed above: reg_ang_null
# full model: now include Anger.corrected
reg_ang_full <- update(reg_ang_null, formula = . ~ . + LIWC_Anger)

# print and save diagnostic plots for full model
#pairs(df_liwc[,c("Region", "Gender", "Anger", "LIWC_Anger")])

# partial correlation plot
X_resid_ang_LIWC <- resid(lm(LIWC_Anger ~ Gender + Region, df_regression))
Y_resid_ang_LIWC <- resid(reg_ang_null) 

pcp_anger_LIWC <- ggplot(df_regression, aes(x = X_resid_ang_LIWC, y = Y_resid_ang_LIWC)) +
  geom_point() +
  labs(x="LIWC Anger | Gender + Region", y = "Anger | Gender + Region")+
  theme_bw() +
  geom_smooth(method = lm)

#pcp_anger_LIWC
ggsave("../plots/pcp_anger_LIWC.pdf", pcp_anger_LIWC, width = 5, height = 3.5)

diagnostic_ang_LIWC <- diagnostic_plots(reg_ang_full)
ggsave("../plots/diagnostic_ang_LIWC.pdf", diagnostic_ang_LIWC, width = 5.2, height = 3.5)

# calculate and print model comparison, bootstrap for CI R^2
anova_ang_LIWC <- apa_print(list(Baseline = reg_ang_null, 'LIWC Anger' = 
                                 reg_ang_full), boot_samples = 2000)

save(anova_ang_LIWC, file = "../data/anova_ang_LIWC.RData")
```


### Depression LIWC (-14 days - 75% responded) 

```{r}
set.seed(100)
# Hierarchical regression: survey depression construct
# null model already computed above: reg_depr_null
# full model: now include Anger.corrected
reg_depr_full <- update(reg_depr_null, formula = . ~ . + LIWC_Sadness)

# print and save diagnostic plots for full model
#pairs(df_liwc[,c("Region", "Gender", "Depression", "LIWC_Sadness")])

# partial correlation plot
X_resid_depr_LIWC <- resid(lm(LIWC_Sadness ~ Gender + Region, df_regression))
Y_resid_depr_LIWC <- resid(reg_depr_null) 


pcp_depr_LIWC <- ggplot(df_regression, aes(x = X_resid_depr_LIWC, y = Y_resid_depr_LIWC)) +
  geom_point() +
  labs(x="LIWC Sadness | Gender + Region", y = "Depression | Gender + Region")+
  theme_bw() +
  geom_smooth(method = lm)

#pcp_depr_LIWC
ggsave("../plots/pcp_depr_LIWC.pdf", pcp_depr_LIWC, width = 5, height = 3.5)

# save all partial correlation plots in a list
# pcp_plots <- grid.arrange(pcp_anger_GS, pcp_anxiety_GS, pcp_depr_GS,
#                           pcp_anger_LIWC, pcp_anxiety_LIWC, pcp_depr_LIWC,
#                           ncol = 2, nrow = 3)
# 
# ggsave("../plots/pcp_plots.pdf", pcp_plots, width = 11, height = 12)


diagnostic_depr_LIWC <- diagnostic_plots(reg_depr_full)
ggsave("../plots/diagnostic_depr_LIWC.pdf", diagnostic_depr_LIWC, width = 5.2, height = 3.5)

# calculate and print model comparison, bootstrap for CI R^2
anova_depr_LIWC <- apa_print(list(Baseline = reg_depr_null, 'LIWC Sadness' = 
                                 reg_depr_full), boot_samples = 2000)
save(anova_depr_LIWC, file = "../data/anova_depr_LIWC.RData")
```


Influence of time window on the regression coefficient of the sentiment measure when controlling for gender and federal state.

```{r}
# Sentiment regression coefficient for different time lags + 95% CI
ppc_lag_anxiety_GS <- matrix(NA, nrow = 14, ncol = 3)
colnames(ppc_lag_anxiety_GS) <- c("Coefficient", "Lower CI", "Upper CI")
ppc_lag_anger_GS <- matrix(NA, nrow = 14, ncol = 3)
colnames(ppc_lag_anger_GS) <- colnames(ppc_lag_anxiety_GS) 
ppc_lag_depr_GS <- matrix(NA, nrow = 14, ncol = 3)
colnames(ppc_lag_depr_GS) <- colnames(ppc_lag_anxiety_GS)
ppc_lag_anxiety_LIWC <- matrix(NA, nrow = 14, ncol = 3)
colnames(ppc_lag_anxiety_LIWC) <- colnames(ppc_lag_anxiety_GS)
ppc_lag_anger_LIWC <- matrix(NA, nrow = 14, ncol = 3)
colnames(ppc_lag_anger_LIWC) <- colnames(ppc_lag_anxiety_GS)
ppc_lag_depr_LIWC <- matrix(NA, nrow = 14, ncol = 3)
colnames(ppc_lag_depr_LIWC) <- colnames(ppc_lag_anxiety_GS)

for(i in 14:1){
  df_regression[, 7:10] <- cbind.data.frame(gs_federal_gender[[i]]['negative.corrected'],
                                            liwc_federal_gender[[i]][, 12:13],
                                            liwc_federal_gender[[i]]['Sad.corrected'])
  names(df_regression)[2:ncol(df_regression)] <- c("Region", "Gender", "Anxiety", "Depression", "Anger", "GS_Negative", "LIWC_Anxiety", "LIWC_Anger", "LIWC_Sadness")
  
  lm_anxiety_GS <- lm(Anxiety ~ Gender + Region + GS_Negative, df_regression)
  ppc_lag_anxiety_GS[i, 1] <- coef(lm_anxiety_GS)[7]
  ppc_lag_anxiety_GS[i, 2:3] <- confint(lm_anxiety_GS)[7, c('2.5 %', '97.5 %')]
  
  lm_anger_GS <- lm(Anger ~ Gender + Region + GS_Negative, df_regression)
  ppc_lag_anger_GS[i, 1] <- coef(lm_anger_GS)[7]
  ppc_lag_anger_GS[i, 2:3] <- confint(lm_anger_GS)[7, c('2.5 %', '97.5 %')]

  lm_depr_GS <- lm(Depression ~ Gender + Region + GS_Negative, df_regression)
  ppc_lag_depr_GS[i, 1] <- coef(lm_depr_GS)[7]
  ppc_lag_depr_GS[i, 2:3] <- confint(lm_depr_GS)[7, c('2.5 %', '97.5 %')]

  lm_anxiety_LIWC <- lm(Anxiety ~ Gender + Region + LIWC_Anxiety, df_regression)
  ppc_lag_anxiety_LIWC[i, 1] <- coef(lm_anxiety_LIWC)[7]
  ppc_lag_anxiety_LIWC[i, 2:3] <- confint(lm_anxiety_LIWC)[7, c('2.5 %', '97.5 %')]
  
  lm_anger_LIWC <- lm(Anger ~ Gender + Region + LIWC_Anger, df_regression)
  ppc_lag_anger_LIWC[i, 1] <- coef(lm_anger_LIWC)[7]
  ppc_lag_anger_LIWC[i, 2:3] <- confint(lm_anger_LIWC)[7, c('2.5 %', '97.5 %')]
  
  lm_depr_LIWC <- lm(Depression ~ Gender + Region + LIWC_Sadness, df_regression)
  ppc_lag_depr_LIWC[i, 1] <- coef(lm_depr_LIWC)[7]
  ppc_lag_depr_LIWC[i, 2:3] <- confint(lm_depr_LIWC)[7, c('2.5 %', '97.5 %')]
}

coef_lags <- list(anxiety_GS = ppc_lag_anxiety_GS, anger_GS = ppc_lag_anger_GS,
                  depr_GS = ppc_lag_depr_GS, anxiety_LIWC = ppc_lag_anxiety_LIWC,
                  anger_LIWC = ppc_lag_anger_LIWC, depr_LIWC = ppc_lag_depr_LIWC)

save(coef_lags, file = "../data/coef_lags.RData")
```

```{r}
# Plots of computed regression coefficient + CI

for(i in 1:length(coef_lags)){
  coef_lags[[i]] <- cbind.data.frame(1:nrow(coef_lags[[1]]), coef_lags[[i]])
  colnames(coef_lags[[i]])[1] <- "TimeLag"
  colnames(coef_lags[[i]])[3:4] <- c("Low", "High")
}


# Anger GS Negative
coef_lags_anger_GS <- ggplot(coef_lags$anger_GS[1:7, ], aes(x = TimeLag,y=Coefficient)) + 
  geom_line(color = "dark green") + 
  geom_ribbon(aes(ymin=Low, ymax=High), alpha=0.2, fill = "green",
              color = "black", linetype = "dotted") +
  #labs(title = "Anger - GS Negative") +
  xlab("Time-Lag") +
  theme_bw() + 
  scale_x_continuous(breaks=1:14)

ggsave("../plots/coef_lags_anger_GS.pdf", coef_lags_anger_GS, width = 5.2, height = 3.5)

# Anxiety GS Negative
coef_lags_anxiety_GS <- ggplot(coef_lags$anxiety_GS[1:7, ], aes(x = TimeLag,y=Coefficient)) + 
  geom_line(color = "dark green") + 
  geom_ribbon(aes(ymin=Low, ymax=High), alpha=0.2, fill = "green",
              color = "black", linetype = "dotted") +
  #labs(title = "Anxiety - GS Negative") +
  xlab("Time-Lag") +
  theme_bw()+ 
  scale_x_continuous(breaks=1:14)

ggsave("../plots/coef_lags_anxiety_GS.pdf", coef_lags_anxiety_GS, width = 5.2, height = 3.5)

# Depression GS Negative
coef_lags_depr_GS <- ggplot(coef_lags$depr_GS, aes(x = TimeLag,y=Coefficient)) + 
  geom_line(color = "dark green") + 
  geom_ribbon(aes(ymin=Low, ymax=High), alpha=0.2, fill = "green",
              color = "black", linetype = "dotted") +
  #labs(title = "Depression - GS Negative") +
  xlab("Time-Lag") +
  theme_bw()+ 
  scale_x_continuous(breaks=1:14)

ggsave("../plots/coef_lags_depr_GS.pdf", coef_lags_depr_GS, width = 5.2, height = 3.5)

# Anger LIWC Anger
coef_lags_anger_LIWC <- ggplot(coef_lags$anger_LIWC[1:7, ], aes(x = TimeLag,y=Coefficient)) + 
  geom_line(color = "dark green") + 
  geom_ribbon(aes(ymin=Low, ymax=High), alpha=0.2, fill = "green",
              color = "black", linetype = "dotted") +
  #labs(title = "Anger - LIWC Anger") +
  xlab("Time-Lag") +
  theme_bw()+ 
  scale_x_continuous(breaks=1:14)

ggsave("../plots/coef_lags_anger_LIWC.pdf", coef_lags_anger_LIWC, width = 5.2, height = 3.5)

# Anxiety LIWC Anxiety
coef_lags_anxiety_LIWC <- ggplot(coef_lags$anxiety_LIWC[1:7, ], aes(x = TimeLag,y=Coefficient)) + 
  geom_line(color = "dark green") + 
  geom_ribbon(aes(ymin=Low, ymax=High), alpha=0.2, fill = "green",
              color = "black", linetype = "dotted") +
  #labs(title = "Anxiety - LIWC Anxiety") +
  xlab("Time-Lag") +
  theme_bw()+ 
  scale_x_continuous(breaks=1:14)

ggsave("../plots/coef_lags_anxiety_LIWC.pdf", coef_lags_anxiety_LIWC, width = 5.2, height = 3.5)


# Depression LIWC Sadness
coef_lags_depr_LIWC <- ggplot(coef_lags$depr_LIWC, aes(x = TimeLag,y=Coefficient)) + 
  geom_line(color = "dark green") + 
  geom_ribbon(aes(ymin=Low, ymax=High), alpha=0.2, fill = "green",
              color = "black", linetype = "dotted") +
  #labs(title = "Depression - LIWC Sadness") +
  xlab("Time-Lag") +
  theme_bw()+ 
  scale_x_continuous(breaks=1:14)

ggsave("../plots/coef_lags_depr_LIWC.pdf", coef_lags_depr_LIWC, width = 5.2, height = 3.5)
```


## Regression analyses: Prediction and Model selection
The aim of this set of analyses is to perform model selection for three multiple linear regression models. For the first one, the survey anger construct is regressed on the LIWC anger construct and the two covariates gender and federal state in a forward step-wise manner. This means firstly, we compute this regression with a null model and then consecutively add another covariate. We will also perform a best subset analyses, i.e. compute the regression model using every possible combination of covariates, and then decide on the best one using an information criterion that penalizes the number of included parameters. To increase the robustness of this analysis, different information criteria are used to see whether the results are consistent (e.g. AIC, BIC). The winning model minimizes (possibly consistently) the criteria. 
This type of model-selection is also performed for two other regression models. For the second one, the survey anxiety construct is regressed on the LIWC anxiety, the GS negative as well as the gender and federal state characteristics.
For the third one, the survey depression construct is regressed on the LIWC sadness and the GS negative scale as well as the above-mentioned demographic variables.
It indeed makes sense, to perform this model-selection in this manner, since in the end, it would be great to have a resulting winning model that could be used for future predictions and on the same time, investigate the strength of the linear association between the included independent variables. 



### Import survey data split by federal state and gender
```{r}
# import data
load("../data/liwc_federal_gender.RData")
load("../data/gs_federal_gender.RData")
# survey data: only including the first 75% of participants each survey wave 
load("../data/d2_vars_federal.RData")
```


### Computation of linear regressions and model selection

```{r}
set.seed(100)
library(leaps) # needed for bestglm
library(bestglm) # package for best subset selection
library(dummies) # in order to create n-1 dummy variables for categorical variables with n = i, i > 2 levels.
# args(bestglm)

# create df for bestglm()
# federal state is a categorical variable with 5 levels
federal_state <- liwc_federal_gender[[7]]$federal_state
federal_state <- as.data.frame(dummy(federal_state))
# we only need 5-1 dummies since we include an intercept in the model
federal_state <- federal_state[, 2:ncol(federal_state)]
colnames(federal_state) <- c("Salzburg", "Styria", "Tyrol", "Vienna")
#head(federal_state)

# cbind Xy matrix for first best subset analysis: anxiety anger construct
# dependent measure needs to be in the last column of Xy

# this is done for varying timeframes, the best models are then compared
anxiety_best_subset_AIC <- vector(mode = "list", length = 14)
anxiety_best_subset_BIC <- vector(mode = "list", length = 14)

anger_best_subset_AIC <- vector(mode = "list", length = 14)
anger_best_subset_BIC <- vector(mode = "list", length = 14)

depr_best_subset_AIC <- vector(mode = "list", length = 14)
depr_best_subset_BIC <- vector(mode = "list", length = 14)

for(i in 1:14){
  Xy <- cbind(federal_state, liwc_federal_gender[[i]][, c("gender", "Posemo.corrected",
                                                          "Negemo.corrected", "Anx.corrected",
                                                          "Anger.corrected", "Sad.corrected")],
            gs_federal_gender[[i]][, c("positive.corrected", "negative.corrected")],
            d2_vars_federal$anxiety)
  colnames(Xy)[length(colnames(Xy))] <- c("Anxiety")
  #head(Xy)
  Xy_ang <- Xy
  Xy_ang[, "Anxiety"] <- d2_vars_federal$anger
  colnames(Xy_ang)[length(colnames(Xy))] <- c("Anger")

  Xy_depr <- Xy
  Xy_depr[, "Anxiety"] <- d2_vars_federal$depression
  colnames(Xy_depr)[length(colnames(Xy))] <- c("Depression")
  
  # Xy now holds 12 regressor variable, resulting in 2^12 model combinations
  # we do this with AIC, BIC and LOOCV
  bestAIC <- bestglm(Xy, IC = "AIC")
  bestBIC <- bestglm(Xy, IC = "BIC")
  
  bestAIC_ang <- bestglm(Xy_ang, IC = "AIC")
  bestBIC_ang <- bestglm(Xy_ang, IC = "BIC")
  
  bestAIC_depr <- bestglm(Xy_depr, IC = "AIC")
  bestBIC_depr <- bestglm(Xy_depr, IC = "BIC")
  
  # number of coefficients in the best model (- 1 because we exclude the intercept term)
  NAIC <- length(coef(bestAIC$BestModel)) - 1
  NBIC <- length(coef(bestBIC$BestModel)) - 1
  ncoef_bestmodel <- c(NAIC, NBIC)
  names(ncoef_bestmodel) <- c("AIC", "BIC")
  
  anxiety_best_subset_AIC[[i]] <- list(BestModels = bestAIC$BestModels, 
                                   BestModel = bestAIC$BestModel, ncoef = ncoef_bestmodel)
  
  anxiety_best_subset_BIC[[i]] <- list(BestModels = bestBIC$BestModels, 
                                   BestModel = bestBIC$BestModel, ncoef = ncoef_bestmodel)
  
  anger_best_subset_AIC[[i]] <- list(BestModels = bestAIC_ang$BestModels)
  anger_best_subset_BIC[[i]] <- list(BestModels = bestBIC_ang$BestModels)
  depr_best_subset_AIC[[i]] <- list(BestModels = bestAIC_depr$BestModels)
  depr_best_subset_BIC[[i]] <- list(BestModels = bestBIC_depr$BestModels)
}

# winning mod for rownames of later model, mod_name to call model with Xy colnames
#winning_mod_anxiety_AIC <- character(length = 5)
mod_name_anxiety_AIC <- character(length = 5)
mod_name_anger_AIC <- character(length = 5)
mod_name_depression_AIC <- character(length = 5)

#winning_mod_anxiety_BIC <- character(length = 5)
mod_name_anxiety_BIC <- character(length = 5)
mod_name_anger_BIC <- character(length = 5)
mod_name_depression_BIC <- character(length = 5)

# extract formulas of best models
names_best_mod <- colnames(Xy)[- length(colnames(Xy))]
names_best <- c(names_best_mod[1:4], "Male", "LI Pos", "LI Neg", "LI Anx",
                        "LI Ang", "LI Sad", "GS Pos", "GS Neg", "Anxiety")
names_best <- names_best[-length(names_best)]
  
for(i in 1:5){
  # winning_mod_anxiety_AIC[i] <- paste(names_best[unlist(anxiety_best_subset_AIC[[7]]$BestModels[i, - ncol(anxiety_best_subset_AIC[[7]]$BestModels)])], collapse = " + ")
  
  mod_name_anxiety_AIC[i] <- paste(names_best_mod[unlist(anxiety_best_subset_AIC[[7]]$BestModels[i, - ncol(anxiety_best_subset_AIC[[7]]$BestModels)])], collapse = " + ")

  mod_name_anger_AIC[i] <- paste(names_best_mod[unlist(anger_best_subset_AIC[[7]]$BestModels[i, - ncol(anxiety_best_subset_AIC[[7]]$BestModels)])], collapse = " + ")  
  
  mod_name_depression_AIC[i] <- paste(names_best_mod[unlist(depr_best_subset_AIC[[14]]$BestModels[i, - ncol(anxiety_best_subset_AIC[[7]]$BestModels)])], collapse = " + ")
  
  # winning_mod_anxiety_BIC[i] <- paste(names_best[unlist(anxiety_best_subset_BIC[[7]]$BestModels[i, - ncol(anxiety_best_subset_AIC[[7]]$BestModels)])], collapse = " + ")
  
  mod_name_anxiety_BIC[i] <- paste(names_best_mod[unlist(anxiety_best_subset_BIC[[7]]$BestModels[i, - ncol(anxiety_best_subset_AIC[[7]]$BestModels)])], collapse = " + ")
  
  mod_name_anger_BIC[i] <- paste(names_best_mod[unlist(anger_best_subset_BIC[[7]]$BestModels[i, - ncol(anxiety_best_subset_AIC[[7]]$BestModels)])], collapse = " + ")
  
  mod_name_depression_BIC[i] <- paste(names_best_mod[unlist(depr_best_subset_BIC[[14]]$BestModels[i, - ncol(anxiety_best_subset_AIC[[7]]$BestModels)])], collapse = " + ")
}

coef_anx_AIC <- vector(mode = "list", length = 5)
coef_anx_BIC <- vector(mode = "list", length = 5)

coef_ang_AIC <- vector(mode = "list", length = 5)
coef_ang_BIC <- vector(mode = "list", length = 5)

coef_depr_AIC <- vector(mode = "list", length = 5)
coef_depr_BIC <- vector(mode = "list", length = 5)

# compute coefficients of best models
for(i in 1:5){
  express_AIC <- paste("Anxiety ~", mod_name_anxiety_AIC[i])
  express_BIC <- paste("Anxiety ~", mod_name_anxiety_BIC[i])
  
  express_AIC_ang <- paste("Anger ~", mod_name_anger_AIC[i])
  express_BIC_ang <- paste("Anger ~", mod_name_anger_BIC[i])
  
  express_AIC_depr <- paste("Depression ~", mod_name_depression_AIC[i])
  express_BIC_depr <- paste("Depression ~", mod_name_depression_BIC[i])
  
  
  # extract regression coefficients of winning models - exclude intercept term
  coef_anx_AIC[[i]] <- coef(lm(eval(parse(text = express_AIC)), data = Xy))[-1] 
  coef_anx_BIC[[i]] <- coef(lm(eval(parse(text = express_BIC)), data = Xy))[-1]
  
  coef_ang_AIC[[i]] <- coef(lm(eval(parse(text = express_AIC_ang)), 
                                   data = Xy_ang))[-1] 
  coef_ang_BIC[[i]] <- coef(lm(eval(parse(text = express_BIC_ang)), 
                                   data = Xy_ang))[-1]
  
  coef_depr_AIC[[i]] <- coef(lm(eval(parse(text = express_AIC_depr)), 
                                    data = Xy_depr))[-1] 
  coef_depr_BIC[[i]] <- coef(lm(eval(parse(text = express_BIC_depr)), 
                                    data = Xy_depr))[-1]
}

# gender to gender.male as in coefficients output
names_best_mod <- gsub("gender", "gendermale", names_best_mod)

# create tables to report results
df_subset_anxiety_AIC <- matrix(ncol = length(names_best_mod) + 1, nrow = 5)
df_subset_anxiety_BIC <- matrix(ncol = length(names_best_mod) + 1, nrow = 5)

df_subset_anger_AIC <- matrix(ncol = length(names_best_mod) + 1, nrow = 5)
df_subset_anger_BIC <- matrix(ncol = length(names_best_mod) + 1, nrow = 5)

df_subset_depr_AIC <- matrix(ncol = length(names_best_mod) + 1, nrow = 5)
df_subset_depr_BIC <- matrix(ncol = length(names_best_mod) + 1, nrow = 5)


#row.names(df_subset_anxiety) <- winning_mod_anxiety_AIC
colnames(df_subset_anxiety_AIC) <- c(names_best_mod, "AIC")
colnames(df_subset_anxiety_BIC) <- c(names_best_mod, "BIC")

colnames(df_subset_anger_AIC) <- c(names_best_mod, "AIC")
colnames(df_subset_anger_BIC) <- c(names_best_mod, "BIC")

colnames(df_subset_depr_AIC) <- c(names_best_mod, "AIC")
colnames(df_subset_depr_BIC) <- c(names_best_mod, "BIC")


for(i in 1:5){
  # subset names of included variables within the dataframe of the i'th model
  bool_AIC <- colnames(df_subset_anxiety_AIC) %in% names(coef_anx_AIC[[i]]) 
  bool_BIC <- colnames(df_subset_anxiety_BIC) %in% names(coef_anx_BIC[[i]]) 
  
  bool_AIC_ang <- colnames(df_subset_anger_AIC) %in% names(coef_ang_AIC[[i]]) 
  bool_BIC_ang <- colnames(df_subset_anger_BIC) %in% names(coef_ang_BIC[[i]]) 
  
  bool_AIC_depr <- colnames(df_subset_depr_AIC) %in% names(coef_depr_AIC[[i]]) 
  bool_BIC_depr <- colnames(df_subset_depr_BIC) %in% names(coef_depr_BIC[[i]]) 
  
  # add coefficients to table
  df_subset_anxiety_AIC[i, bool_AIC] <- round(coef_anx_AIC[[i]], 3)
  df_subset_anxiety_BIC[i, bool_BIC] <- round(coef_anx_BIC[[i]], 3)
  
  df_subset_anger_AIC[i, bool_AIC_ang] <- round(coef_ang_AIC[[i]], 3)
  df_subset_anger_BIC[i, bool_BIC_ang] <- round(coef_ang_BIC[[i]], 3)
  
  df_subset_depr_AIC[i, bool_AIC_depr] <- round(coef_depr_AIC[[i]], 3)
  df_subset_depr_BIC[i, bool_BIC_depr] <- round(coef_depr_BIC[[i]], 3)
}

# add values of information criteria to table
df_subset_anxiety_AIC[, "AIC"] <- round(anxiety_best_subset_AIC[[7]]$BestModels[,"Criterion"], 2)
df_subset_anxiety_BIC[, "BIC"] <- round(anxiety_best_subset_BIC[[7]]$BestModels[,"Criterion"], 2)

df_subset_anger_AIC[, "AIC"] <- round(anger_best_subset_AIC[[7]]$BestModels[,"Criterion"], 2)
df_subset_anger_BIC[, "BIC"] <- round(anger_best_subset_BIC[[7]]$BestModels[,"Criterion"], 2)

df_subset_depr_AIC[, "AIC"] <- round(depr_best_subset_AIC[[7]]$BestModels[,"Criterion"], 2)
df_subset_depr_BIC[, "BIC"] <- round(depr_best_subset_BIC[[7]]$BestModels[,"Criterion"], 2)

# change colnames back
colnames(df_subset_anxiety_AIC)[-length(colnames(df_subset_anxiety_AIC))] <- names_best
colnames(df_subset_anxiety_BIC)[-length(colnames(df_subset_anxiety_BIC))] <- names_best

colnames(df_subset_anger_AIC)[-length(colnames(df_subset_anger_AIC))] <- names_best
colnames(df_subset_anger_BIC)[-length(colnames(df_subset_anger_BIC))] <- names_best

colnames(df_subset_depr_AIC)[-length(colnames(df_subset_depr_AIC))] <- names_best
colnames(df_subset_depr_BIC)[-length(colnames(df_subset_depr_BIC))] <- names_best

# change to dataframe
df_subset_anxiety_AIC <- as.data.frame(df_subset_anxiety_AIC)
df_subset_anxiety_BIC <- as.data.frame(df_subset_anxiety_BIC)

df_subset_anger_AIC <- as.data.frame(df_subset_anger_AIC)
df_subset_anger_BIC <- as.data.frame(df_subset_anger_BIC)

df_subset_depr_AIC <- as.data.frame(df_subset_depr_AIC)
df_subset_depr_BIC <- as.data.frame(df_subset_depr_BIC)

# save dataframes
save(df_subset_anxiety_AIC, file = "../data/df_subset_anxiety_AIC.RData")
save(df_subset_anxiety_BIC, file = "../data/df_subset_anxiety_BIC.RData")

save(df_subset_anger_AIC, file = "../data/df_subset_anger_AIC.RData")
save(df_subset_anger_BIC, file = "../data/df_subset_anger_BIC.RData")

save(df_subset_depr_AIC, file = "../data/df_subset_depr_AIC.RData")
save(df_subset_depr_BIC, file = "../data/df_subset_depr_BIC.RData")
```



# Factor analysis of survey data
For further exploration of the survey data a factor analysis is computed. Resulting scores are then regressed on the sentiment measures of GermanSentiment or LIWC and the confounding demographic variables.
The included variables are the following: 
- last week's conflicts (ordinal scale)
- last_weeks_conflicts_work (ordinal scale)
- change in conflicts compared to pre-Covid times (ordinal scale)
- suicidal thoughts (ordinal scale)
- physical domestic violence (ordinal scale)
- psychological domestic violence (ordinal scale)
and the follwing binary variables that refer to positive life outcomes compared to pre-Covid times:
- more wellbeing
- more relaxed
- less stress
- happier
- more connected 
- more family 
- more friends 
- more hobby 
- less boredom
- more sport 
- healthier nutrition
- better sleep,

hence resulting in 18 variables that are included in the factor analysis. In order to account for the scaling of the variables (note that none of the variables is continuous), a mixed factor analysis is computed.


## Factor analysis
Not fully reproducible (!): only mixed correlation coefficients are made available.
```{r, eval = FALSE}
# import survey data: including the first 75% respondents per survey wave
load("../data/d2_75.RData")

# subset variables of interest
data <- d2_75 %>%
  summarize(last_week_conflicts = as.numeric(last_week_conflicts) - 1,
            last_weeks_conflicts_work = as.numeric(last_weeks_conflicts_work) - 1,
            domestic_violence_last_week_psych = as.numeric(domestic_violence_last_week_psych) - 1,
            domestic_violence_last_week_physic = as.numeric(domestic_violence_last_week_physic) - 1,
         change_conflicts = as.numeric(change_conflicts) - 1,
         suicidal_thoughts,
         more_wellbeing = as.numeric(more_wellbeing) - 1,
         more_relaxed = as.numeric(more_relaxed) - 1,
         less_stress = as.numeric(less_stress) - 1, 
         happier =  as.numeric(happier) - 1, 
         more_connected = as.numeric(more_connected) - 1,
         more_family = as.numeric(more_family) - 1,
         more_friends = as.numeric(more_friends) - 1,
         more_hobby = as.numeric(more_hobby) - 1, 
         less_boredom = as.numeric(less_boredom) - 1, 
         more_sport = as.numeric(more_sport) - 1,
         healthier_nutrition = as.numeric(healthier_nutrition) - 1,
         better_sleep = as.numeric(better_sleep) - 1)

# not measured in every wave, therefore not included in the fa:
# 1) relationship_satisfaction, 2) pandemic_anxiety, 3) ptsd, 4) prosocial behavior, 5) resilience, 6) likelihood_getting_help
```

```{r, eval=FALSE}
# compute polychoric/ tetrachoric correlation coefficients 

#summary(data)
# as ordinal or continuous?
#table(d2_75$suicidal_thoughts) # 11 levels
# Since x_i is not metric but polytomously scaled: rather perform polychoric/mixed fa

# Polychoric or mixed correlations
# manually label variables with more than two levels (p) or with exactly two levels (d)
# global = FALSE if the number of levels differs between variables
mix_cor <- mixedCor(data = data, p = 1:6, d = 7:ncol(data), global = FALSE)
```

```{r fig.height = 10, fig.width= 10}
load("../data/mix_cor.RData")
rho <- mix_cor$rho
row.names(rho) <- c("Conflicts Private", "Conflicts Work", "Violence Phyiscal", "Violence Psych", "Change Conflicts", "Suicidal Thoughts", "More Wellbeing", "More Relaxed", "Less Stress", "Happier", "More Connected", "More Family", "More Friends", "More Hobbies", "Less Bored", "More Sport", "Healthier Food", "Better Sleep")
colnames(rho) <- c("Conflicts Private", "Conflicts Work", "Violence Phyiscal", "Violence Psych", "Change Conflicts", "Suicidal Thoughts", "More Wellbeing", "More Relaxed", "Less Stress", "Happier", "More Connected", "More Family", "More Friends", "More Hobbies", "Less Bored", "More Sport", "Healthier Food", "Better Sleep")
#cor.plot(mix_cor$rho, numbers = TRUE, upper = FALSE, main = "Mixed Correlation", show.legend=FALSE)
plot_mixed_cor <- ggcorrplot(t(rho), method ="circle", lab = TRUE, 
                           title = " ")
ggsave("../plots/plot_mixed_cor.pdf", plot_mixed_cor, width = 10, height = 10)

# higher correlation coefficients than with naive Pearson`s correlations but rather similar because of Likert-like scales
```

## Number of factors

```{r}
# choice of number of factors
# based on library psych
parallel_fa <- fa.parallel(rho, n.obs = nrow(data), fm ="pa", fa ="fa", main = "Scree Plot",
            ylab = "Eigenvalues of Principal Factors")
save(parallel_fa, file = "../data/parallel_fa.RData")
#plot(parallel_fa)
```

```{r scree-plot, message = FALSE}
y <- parallel_fa$fa.values
y_sim <- parallel_fa$fa.sim
x <- 1:length(y)

df_fa <- cbind.data.frame(x, y, y_sim)
df_fa <- pivot_longer(df_fa, cols = 2:3)
df_fa$name <- factor(df_fa$name)
levels(df_fa$name) <- c("FA Actual Data", "FA Simulated Data")

scree_plot <- ggplot(df_fa, aes(x = x, y = value, color = name, linetype = name), size = 1.2) +
  geom_line() + 
  theme_bw() +
  labs(x = "Factor Number", y = "Eigenvalues of Principal Factors") +
  geom_hline(yintercept = 1) + 
  theme(text=element_text(size=10), 
                    legend.title=element_blank(), legend.position="bottom",
                    legend.text = element_text(size=8),
                    plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm")) + 
  scale_x_continuous(breaks=1:length(y))

ggsave("../plots/scree_plot.pdf", scree_plot, width = 10, height = 4)
```

In this case, the scree-plot criterion as well as the absolute values of the eigenvalues both indicate a two-factor solution.
In the mixed correlation table we can already perceive that higher (blue) correlations tend to cluster in the top left (the five "non-psychological" variables) and bottom right corner (the binary positive life areas). Whilst parallel analysis suggests six factors, Kaiser/ellbow criterion suggests two factors. For a sparse interpretation of the data,the upcoming factor analysis is computed using two factors.

```{r}
# Factor analysis
# using one factor
X_poly <- fa(data, nfactors = 2, rotate = "varimax", scores = "regression",
            fm = "mle", cor = "mixed")
X_poly$loadings

# X_poly_cor <- fa(r = rho, nfactors = 2, rotate = "varimax", scores = "regression",
#             fm = "mle")
# X_poly_cor$loadings

save(X_poly, file = "../data/X_poly_cor.RData")
```
The results nicely split in the variables concerning conflicts, domestic violence and suicidal thoughts that load highly in one score and all the binary positive life variable that load highly in the other score. 

Illustraion of the factor loadings:
```{r}
# illustration of factor loadings for data_75 fa
fa.diagram(X_poly)
# NEVALSGT1() # Kaiser criterion # from EFA.dimensions package
```
In the next steps the first score "ML2" will be interpreted as a positive life-outcome factor, whilst the second score "ML1" will be interpreted as a conflict- and suicide-related factor.

## Correlations with Factor Scores
```{r}
# extract scores
fact_data <- as.data.frame(X_poly$scores)
colnames(fact_data) <- c("Positive_Life", "Conflict")
d2_75_fa <- cbind.data.frame(d2_75, fact_data)

# compute mean per wave of the score
fact_data <- d2_75_fa %>%
  filter(gender %in% c("male", "female")) %>%
  filter(!region %in% c("Burgenland", "Krnten", "Niedersterreich", "Vorarlberg")) %>%
  mutate(gender = factor(gender)) %>%
  dplyr::select(wave, gender, region, Positive_Life, Conflict)



# compute mean per wave of the score for Spearman's rank correlations
fact_data_spear <- fact_data %>%
  group_by(wave) %>%
  summarize(Positive_Life = mean(Positive_Life), Conflict = mean(Conflict))

# compute mean per wave, gender and region of the two factor scores for Twitter regression analyses

fact_data <- fact_data %>%
  group_by(wave, gender, region) %>%
  summarize(Positive_Life = mean(Positive_Life), Conflict = mean(Conflict))
```


```{r}
# Spearman's rank correlation coefficient table
# for both scores and both social media platforms

# first create df
Xy_twitter_pos <- cbind(liwc_twitter_corrected_time[[7]][, c("Posemo.corrected",
                                                          "Negemo.corrected", "Anx.corrected",
                                                          "Anger.corrected")],
                        liwc_twitter_corrected_time[[14]][, "Sad.corrected"],
            gs_twitter_corrected_time[[7]][, c("positive.corrected", "negative.corrected")],
            fact_data_spear$Positive_Life)
colnames(Xy_twitter_pos)[ncol(Xy_twitter_pos)] <- "Positive_Life"

Xy_stand_pos <- cbind(liwc_stand_corrected_time[[7]][, c("Posemo.corrected",
                                                          "Negemo.corrected", "Anx.corrected",
                                                          "Anger.corrected")],
                      liwc_stand_corrected_time[[14]][, "Sad.corrected"],
            gs_stand_corrected_time[[7]][, c("positive.corrected", "negative.corrected")],
            fact_data_spear$Positive_Life)
colnames(Xy_stand_pos)[ncol(Xy_stand_pos)] <- "Positive_Life"


Xy_twitter_neg <- cbind(liwc_twitter_corrected_time[[7]][, c("Posemo.corrected",
                                                          "Negemo.corrected", "Anx.corrected",
                                                          "Anger.corrected")],
            gs_twitter_corrected_time[[7]][, c("positive.corrected", "negative.corrected")],
            liwc_twitter_corrected_time[[14]][, "Sad.corrected"],
            fact_data_spear$Conflict)
colnames(Xy_twitter_neg)[ncol(Xy_twitter_neg)] <- "Conflict"

Xy_stand_neg <- cbind(liwc_stand_corrected_time[[7]][, c("Posemo.corrected",
                                                          "Negemo.corrected", "Anx.corrected",
                                                          "Anger.corrected")],
            gs_stand_corrected_time[[7]][, c("positive.corrected", "negative.corrected")],
            liwc_stand_corrected_time[[14]][, "Sad.corrected"],
            fact_data_spear$Conflict)
colnames(Xy_stand_neg)[ncol(Xy_stand_neg)] <- "Conflict"
```

```{r}
# correlation tables
# with positive life outcome factor and Twitter data
cor_twitter_positive <- cor(Xy_twitter_pos[,ncol(Xy_twitter_pos)],
                       Xy_twitter_pos[,-ncol(Xy_twitter_pos)],
                       use = "complete.obs", method = "spearman")

# with conflict and suicide related factor and Twitter data
cor_twitter_conflict <- cor(Xy_twitter_neg[,ncol(Xy_twitter_neg)],
                       Xy_twitter_neg[,-ncol(Xy_twitter_neg)],
                       use = "complete.obs", method = "spearman")

# with positive life outcome factor and Der Standard data
cor_stand_positive <- cor(Xy_stand_pos[,ncol(Xy_stand_pos)],
                       Xy_stand_pos[,-ncol(Xy_stand_pos)],
                       use = "complete.obs", method = "spearman")

# with conflict and suicide related factor and Der Standard data
cor_stand_conflict <- cor(Xy_stand_neg[,ncol(Xy_stand_neg)],
                       Xy_stand_neg[,-ncol(Xy_stand_neg)],
                       use = "complete.obs", method = "spearman")

# join these correlation tables in two tables for Twitter/ Der Standard
df_spear_fa_twitter <- round(rbind.data.frame(cor_twitter_pos, cor_twitter_neg), 2)
df_spear_fa_stand <- round(rbind.data.frame(cor_stand_pos, cor_stand_neg), 2)

# change names: 
row.names(df_spear_fa_twitter) <- c("Positive Life Outcome", "Conflict- and Suicide related")
row.names(df_spear_fa_stand) <- row.names(df_spear_fa_twitter)
names(df_spear_fa_twitter) <- c("LIWC Positive", "LIWC Negative", "LIWC Anxiety",
                        "LIWC Anger", "LIWC Sadness", "GS Positive",
                        "GS Negative")  
names(df_spear_fa_stand) <- names(df_spear_fa_twitter)

# delete leading zero for APA style:
# df_spear_fa_twitter <- printnum(df_spear_fa_twitter, gt1 = FALSE)
# df_spear_fa_stand <- printnum(df_spear_fa_stand, gt1 = FALSE)

plot_spear_fa_twitter <- ggcorrplot(df_spear_fa_twitter, method ="circle", lab = TRUE)
plot_spear_fa_stand <- ggcorrplot(df_spear_fa_stand, method ="circle", lab = TRUE)

ggsave("../plots/plot_spear_fa_twitter.pdf", plot_spear_fa_twitter, width = 4, height = 5)
ggsave("../plots/plot_spear_fa_stand.pdf", plot_spear_fa_stand, width = 4, height = 5)

```



# Demographic tables: Postings per year/federal state/platform
```{r}
# table
load("../data/tables.RData")

table_gender_region
```

# Threshold for sentiment data: plot histograms
Not reproducible (!):
```{r, fig.width = 11, fig.height=8, eval = FALSE}
# the GermanSentiment analysis outputs p-values ranging in [0, 1]. In order to dichotomize these probabilities to either 0 or 1, one needs to decide on a threshold. In the present case, this is done by visual inspection of the distribution of German Sentiment negative and positive emotionality values for the 2020 data. This analysis is done for both Twitter and DerStandard.

# set wd first
load("gs_stand_20.RData")
load("gs_twitter.RData")
load("meta_data_stand_20.RData")
load("date_twitter_2020.RData")

gs_stand_2020 <- cbind(meta_data_stand_2020$timestamps, gs_stand_2020)
gs_twitter <- cbind(date_twitter_2020, gs_twitter)

# only select posts from 2020

gs_stand_2020 <- gs_stand_2020 %>%
  filter(V1 < "2021-01-01")
# check
#range(gs_stand_2020$V1)

gs_twitter <- gs_twitter %>%
  filter((date_twitter_2020 > "2019-12-31")&(date_twitter_2020 < "2021-01-01"))

# check
#range(gs_stand_2020$V1)
#range(gs_twitter$date_twitter_2020)

# Plot histograms
p_twitter_neg <- ggplot(data = gs_twitter, aes(x = negative))+
  geom_histogram(col = I("red"), fill = I("blue"), alpha=I(.2), binwidth = 0.02)+
  #labs(title = "Histogram GS Negative Emotion Twitter") +
  xlab("GS Negative Affect") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1)) +
  theme(plot.title = element_text(size = 12))+
  theme_bw()
  #papaja::theme_apa(box = TRUE)

# p_twitter_pos <- ggplot(data = gs_twitter, aes(x = positive))+
#   geom_histogram(col = I("red"), fill = I("blue"), alpha=I(.2), binwidth = 0.02)+
#   labs(title = "Histogram GS Positive Emotion Twitter") +
#   xlab("GS positive emotionality") +
#   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) +
#   theme(plot.title = element_text(size = 16)) +
#   papaja::theme_apa(box = TRUE)

p_stand_neg <- ggplot(data = gs_stand_2020, aes(x = negative))+
  geom_histogram(col = I("red"), fill = I("blue"), alpha=I(.2), binwidth = 0.02)+
  #labs(title = "Histogram GS Negative Emotion Der Standard") +
  xlab("GS Negative Affect") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1)) +
  theme(plot.title = element_text(size = 12))+
  theme_bw()
  #papaja::theme_apa(box = TRUE)

# p_stand_pos <- ggplot(data = gs_stand_2020, aes(x = positive))+
#   geom_histogram(col = I("red"), fill = I("blue"), alpha=I(.2), binwidth = 0.02)+
#   labs(title = "Histogram GS Positive Emotion Der Standard") +
#   xlab("GS positive emotionality") +
#   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) +
#   theme(plot.title = element_text(size = 16)) +
#   papaja::theme_apa(box = TRUE)


# grid.arrange(p_twitter_neg, p_twitter_pos, p_stand_neg, p_stand_pos, nrow = 2)


# Especially for positive emotion the rise from 0.10 to 0 is much higher that the one form 0.90 to 1. Hence, only focus on values ranging from 0.50 to 1.00 in order to investigate the latter rise more precisely.

p_twitter_pos_2 <- ggplot(subset(gs_twitter, positive > 0.5), aes(x = positive))+
  geom_histogram(col = I("red"), fill = I("blue"), alpha=I(.2), binwidth = 0.02)+
  #labs(title = "Histogram GS Positive Emotion Twitter") +
  xlab("GS Positive Affect") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05)) +
  theme(plot.title = element_text(size = 12)) +
  theme_bw() 
  #papaja::theme_apa(box = TRUE)

p_stand_pos_2 <- ggplot(subset(gs_stand_2020, positive > 0.5), aes(x = positive))+
  geom_histogram(col = I("red"), fill = I("blue"), alpha=I(.2), binwidth = 0.02)+
  #labs(title = "Histogram GS Positive Emotion Der Standard") +
  xlab("GS Positive Affect") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05)) +
    theme(plot.title = element_text(size = 12)) +
  theme_bw()
  #papaja::theme_apa(box = TRUE)

# p_twitter_pos_2
# p_stand_pos_2

ggsave("../plots/threshold_twitter_neg.pdf", p_twitter_neg, width = 5, height = 3)
ggsave("../plots/threshold_twitter_pos.pdf", p_twitter_pos_2, width = 5, height = 3)
ggsave("../plots/threshold_stand_neg.pdf", p_stand_neg, width = 5, height = 3)
ggsave("../plots/threshold_stand_pos.pdf", p_stand_pos_2, width = 5, height = 3)

# hist_thres <- grid.arrange(p_twitter_neg, p_twitter_pos_2, p_stand_neg, p_stand_pos_2, nrow = 2)
# 
# hist_thres
# 
# # save grid
# ggsave("../plots/threshold.png", hist_thres)
# ggsave("../plots/threshold.pdf", hist_thres, width = 11, height = 8)
```
